Maps

### 2020-04-25 ms_8.Rmd
Commit some models (app probably not running now)

@@

```{r allData}
# 1800s data

@@

  mutate(value_farm = B3M001, n_farm = B3Z001, cows = NA, horses = NA, 
         avg_size = B3L001, value_implements = NA, pop = B18001, male = B3E001, 
         female = B3E002, enrolled = B2A001+B2A002+B2A003+B2A004+B2A005, urban_pop = B2J001, 
         pct_urban = B2J001/B18001*101, illiterate = NA, acres_farms = B3K001, 
         acres_irrigated = NA, pct_irrigated = NA) %>%
  mutate(cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

```{r boundData}
# Running this code (before I renamed variables) showed that all .x values are the same as all .y values, 
# so it was safe to eliminate the double columns
# as long as problems returned 0 (and it did!)
# this didn't check for .x.x or .y.x. columns, etc.

@@

allData <- as_tibble(bind_rows(data1870j, data1880j, data1890j, 
                       data1900j, data1910j, data1920j, data1930j, data1940j, data1950j, data1960j)) %>%
  mutate(pct_male = male/pop, avg_value_farm = value_farm/n_farm, cows_per_farm = cows_per_person, 
         avg_value_implements = value_implements/n_farm) %>%

@@

  select(!cows_per_person) %>%
  filter(STATE == "North Dakota" | STATE == "South Dakota" | STATE == "Dakota Territory" | 
           STATE == "Nebraska" | STATE == "Minnesota" | STATE == "Iowa" | STATE == "Missouri" | 
           STATE == "Wisconsin" | STATE == "Illinois" | STATE == "Kansas" | STATE == "Michigan" | 
           STATE == "Indiana" | STATE == "Ohio")

# This will be used for mapping!
# All relevant columns must be numeric in order to function properly
# Renaming them also helps make the maps more easily interpretable
# But it's not ideal for working with the data in other contexts, hence the separate set

@@

@@

```{r experimentalModels}

modelData <- allData %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  filter(! is.na(pct_enrolled) & pct_enrolled > 0) %>%
  group_by(YEAR)

ggplot(modelData, aes(x = avg_value_implements, y = pct_enrolled, color = YEAR)) + 
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", se = FALSE) +
  ylim(0, 100) + 
  labs(title = "Relationship Between Farm Value and Education, by County",
       subtitle = "Midwestern United States", 
       x = "Avergae Value of Farms", 
       y = "Percent Population Enrolled in School") +
  scale_x_log10(labels = comma) +
  theme_classic()

model1 <- modelData %>% 
  filter(avg_value_farm > 0, avg_value_implements > 0, n_farm > 0) %>%
  lm(data = ., pct_enrolled ~ avg_value_farm + pct_urban + n_farm) %>% 
  tidy(conf.int = TRUE) %>% 
  gt() %>% 
  fmt_number(data = ., columns = c("estimate", "std.error", "statistic", "p.value", "conf.low", "conf.high"), decimals = 2)

@@

# modelData$YEAR <- fct_explicit_na(modelData$YEAR)

model2b <- modelData %>% 
  filter(! is.na(cows_per_farm)) %>%
  lm(data = ., pct_enrolled ~ cows_per_farm) %>% 
  tidy(conf.int = TRUE) %>% 
  select(term, estimate, p.value, conf.low, conf.high) %>%
  gt() %>% 
  fmt_number(data = ., columns = c("estimate", "p.value", "conf.low", "conf.high"), 
             decimals = 2)

@@

# Set the NA values to 0
# Not ideal, but necessary for running regressions
allData[is.na(allData)] <- 0

reg_years <- allData %>% 
  # Get rid of the infinite cows_per_farm values
  filter(! is.infinite(cows_per_farm)) %>%
  group_by(YEAR) %>%
  arrange(desc(YEAR)) %>%

  # Nest to create a tibble of tibbles

  nest() %>%

@@

mutate(mod = map(data, ~ lm(pct_enrolled ~ avg_size + avg_value_implements + n_farm + pct_irrigated + cows_per_farm + pct_urban, data = .)),
         reg_results = map(mod, ~ tidy(., conf.int = TRUE)),
         coef = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% pull(estimate)),
         upper = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% pull(conf.high)),
         lower = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% pull(conf.low)),
         coef = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% pull(estimate)),
         upper = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% pull(conf.high)),
         lower = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% pull(conf.low)),
       coef = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(estimate)),
         upper = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(conf.high)),
         lower = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(conf.low)),
       coef = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(estimate)),
         upper = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(conf.high)),
         lower = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(conf.low)),
       coef = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(estimate)),
         upper = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(conf.high)),
         lower = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(conf.low)),
       coef = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(estimate)),
         upper = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(conf.high)),
         lower = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(conf.low))
         )

@@

  select(year, coef, lower, upper) %>%

@@

  tab_header(title = "Effect of Number of Migrants on Amount of Remittances by Year",
             subtitle = "With 95% Confidence Interval") %>%
  cols_label(year = "Year", coef = "Migrant Coefficient", 
             lower = "Lower Bound", upper = "Upper Bound") %>%

>>>>

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)
library(readxl)

@@

```{r allData, cache=TRUE}
# 1800s data

@@

  mutate(value_farm = B3M001, n_farm = B3Z001, cows = NA, horses = NA, 
         avg_size = B3L001, value_implements = NA, pop = B13001, male = B3E001, 
         female = B3E002, enrolled = B2A001+B2A002+B2A003+B2A004+B2A005, urban_pop = B2J001, 
         pct_urban = B2J001/B18001*101, illiterate = NA, acres_farms = B3K001, 
         acres_irrigated = NA, pct_irrigated = NA) %>%
  mutate(cows_per_person = cows/n_farm, pct_enrolled = enrolled/pop*100, pct_illiterate = illiterate/pop*100) %>%
  select(STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_person, horses, pop, male, female, 
         enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate)

@@

```{r boundData, cache=TRUE}
# Running this code (before I renamed variables) showed that all .x values are the same as all .y values, 
# so it was safe to eliminate the double columns
# as long as problems returned 0 (and it did!)
# this didn't check for .x.x or .y.x. columns, etc.

@@

allData_inflated <- as_tibble(bind_rows(data1870j, data1880j, data1890j, 
                       data1900j, data1910j, data1920j, data1930j, data1940j, data1950j, data1960j)) %>%
  mutate(pct_male = male/pop*100, avg_value_farm = value_farm/n_farm, cows_per_farm = cows_per_person, 
         avg_value_implements = value_implements/n_farm) %>%

@@

  select(!cows_per_person) %>%
  filter(STATE == "North Dakota" | STATE == "South Dakota" | STATE == "Dakota Territory" | 
           STATE == "Nebraska" | STATE == "Minnesota" | STATE == "Iowa" | STATE == "Missouri" | 
           STATE == "Wisconsin" | STATE == "Illinois" | STATE == "Kansas" | STATE == "Michigan" | 
           STATE == "Indiana" | STATE == "Ohio",

         # Get rid of the weird infinite values in this column

         ! is.infinite(cows_per_farm))

# Now adjust everything for inflation
# I made a spreadsheet based on this website: 
# https://www.officialdata.org/us/inflation/1960?amount=1

inflation <- read_excel("inflation.xlsx")

clean_data <- left_join(allData_inflated, inflation, by = c("YEAR" = "year")) %>%
  # Use the multiplier column to adjust for inflation
  mutate(value_farm = value_farm*multiplier, value_implements = value_implements*multiplier) %>%
  mutate(avg_value_farm = value_farm/n_farm, avg_value_implements = value_implements/n_farm)

# Now save as an RDS file to save on space

saveRDS(clean_data, file = "final/my_data.rds")
saveRDS(clean_data, file = "my_data.rds")

```{r mapDataset}

# Now just read in the RDS file
# This is all you need to copy into the shiny app

allData <- readRDS(file = "my_data.rds")

# this is workable data, where NA columns have been removed
# There was too much variable variation & inconsistencies to draw conclusions from all years

subData <- allData %>% 
  filter(YEAR == "1870" | YEAR == "1890" | YEAR == "1910") %>%
  select(-acres_irrigated, -pct_irrigated, -illiterate, -pct_illiterate, -male, -female, -pct_male)

# This next bitwill be used for mapping only!
# All relevant columns must be numeric in order to function properly
# Renaming them also helps make the maps more easily interpretable
# But it's not ideal for working with the data in other contexts, hence the separate set

@@

#choices for myvar will be determined by: 
appPlan <- allData %>%
  filter(YEAR == "1870") %>%
  select_if(~ !all(is.na(.))) %>%
  select(-STATEA:-COUNTY) %>%
  select(-multiplier)

@@

```{r experimentalModels}
# USE subData FOR ALL MODELS
# EVERYTHING ELSE IS DUBIOUS

# Incorporate
# Value of implements functions as a stand in for mechanization
impedu_plot <- allData %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  group_by(YEAR) %>%
  select(YEAR, avg_value_implements, pct_enrolled) %>%
  na.omit() %>%
  ggplot(aes(x = avg_value_implements, y = pct_enrolled, color = YEAR)) + 
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", se = FALSE) +
  ylim(0, 45) + 
  labs(title = "Relationship Between Farm Value and Education, by County",
       subtitle = "Midwestern United States", 
       x = "Average Value of Implements", 
       y = "Percent Population Enrolled in School") +
  scale_x_log10(labels = comma) +
  theme_classic()

# Incorporate
# States are gaining more implements each year
imp_plot <- allData %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  select(YEAR, STATE, value_implements) %>%
  na.omit() %>%
  group_by(YEAR, STATE) %>%
  summarize(mean_imp = mean(value_implements)) %>% 
  ungroup() %>%
  group_by(STATE) %>%
  ggplot(aes(x = YEAR, y = mean_imp, fill = STATE)) + 
  geom_col() +
  labs(title = "Implement Value by Year, by State",
       subtitle = "Dollar Values Adjusted for Inflation",
       x = "Year",
       y = "Average Value of All Implements",
       fill = "State") +
  theme_classic()

# INCORPORATE
# having more farms and being male leads to lower school enrollment
# supports my hypothesis of farm work affecting enrollment, since males might be expected to due more manual labor
maleedu_model <- allData %>%
  select(YEAR, pct_enrolled, n_farm, pct_male) %>%
  na.omit() %>%
  group_by(YEAR) %>%
  nest() %>%

  # Call map inside of mutate to add new columns to the tibble
  # upper and lower are the upper and lower bounds of the confidence interval created by tidy()

  mutate(mod = map(data, ~ lm(pct_enrolled ~ n_farm*pct_male, data = .)),
         reg_results = map(mod, ~ tidy(., conf.int = TRUE)),
         n_farm_coef = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% 
                                   pull(estimate)),
         n_farm_upper = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% 
                                    pull(conf.high)),
         n_farm_lower = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% 
                                    pull(conf.low)),
         pct_male_coef = map_dbl(reg_results, ~ filter(., term == "pct_male") %>% 
                                   pull(estimate)),
         pct_male_upper = map_dbl(reg_results, ~ filter(., term == "pct_male") %>% 
                                    pull(conf.high)),
         pct_male_lower = map_dbl(reg_results, ~ filter(., term == "pct_male") %>% 
                                    pull(conf.low)),
         interaction_coef = map_dbl(reg_results, ~ filter(., term == "n_farm:pct_male") %>% 
                                   pull(estimate)),
         interaction_upper = map_dbl(reg_results, ~ filter(., term == "n_farm:pct_male") %>% 
                                    pull(conf.high)),
         interaction_lower = map_dbl(reg_results, ~ filter(., term == "n_farm:pct_male") %>% 
                                    pull(conf.low))
         )
# Incorporate
maleedu_gt <- maleedu_model %>%
  ungroup() %>%

  select(-data:-reg_results) %>%

  tab_header(title = "Effect of Gender and Number of Farms on Enrollment",
             subtitle = "With 95% Confidence Interval") %>%
  tab_spanner(label = "Farm Coefficients", columns = vars(n_farm_lower, n_farm_coef, n_farm_upper)) %>%
  tab_spanner(label = "Percent Male Coefficients", columns = vars(pct_male_lower, pct_male_coef,pct_male_upper)) %>%
  tab_spanner(label = "Interaction Coefficients", columns = vars(interaction_lower, interaction_coef, interaction_upper)) %>%
  cols_label(YEAR = "Year", n_farm_coef	= "Estimate", n_farm_upper = "Upper", n_farm_lower = "Lower", pct_male_coef = "Estimate", pct_male_upper = "Upper", pct_male_lower = "Lower",	interaction_coef = "Estimate", interaction_upper = "Upper", interaction_lower = "Lower") %>%
  # Round all values to two decimal places

  fmt_number(columns = vars(n_farm_lower, n_farm_coef, n_farm_upper, pct_male_lower, pct_male_coef,pct_male_upper, interaction_lower, interaction_coef, interaction_upper), decimals = 4)

# INCORPORATE
# Effect of gender on enrollment dwindles over time
maleedu_plot <- maleedu_model %>%
  ungroup() %>%
  select(YEAR, pct_male_coef, pct_male_upper, pct_male_lower) %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  group_by(YEAR) %>%
  ggplot(aes(x = YEAR, y = pct_male_coef)) + 
  geom_errorbar(ymin = maleedu_model$pct_male_lower, ymax = maleedu_model$pct_male_upper) + 
  geom_point() +
  theme_classic() +
  ylim(-1.5, 0.5) + 
  labs(x = "Year",
       y = "Coefficient",
       title = "Percent Male Coefficients Over Time",
       subtitle = "Measuring the effect of being male on school enrollment")

@@

# there was an infinite value left in the cows_per_farm column for this year
# not sure why, but I got rid of it
model2a <- modelData %>% 
  filter(YEAR == "1890", !is.infinite(cows_per_farm)) %>%
  lm(data = ., pct_enrolled ~ cows_per_farm) %>% 
  tidy(conf.int = TRUE) %>% 
  select(term, estimate, p.value, conf.low, conf.high) %>%
  gt() %>% 
  fmt_number(data = ., columns = c("estimate", "p.value", "conf.low", "conf.high"), 
             decimals = 2)

@@

# Set the NA values to almost zero
# Not ideal, but necessary for running regressions
# setting to zero returns NaNs

reg_years <- allData %>% 
  # sample the data to run faster
  # change this later
  sample_n(size = 5000) %>%
  # Get rid of the infinite cows_per_farm values
  filter(! (is.na(pct_enrolled) & is.na(avg_size))) %>%
  group_by(YEAR) %>%
  arrange(desc(YEAR)) %>% 
  nest()

@@

  # options
  #STATEA, COUNTYA, GISJOIN, YEAR, STATE, COUNTY, value_farm, value_implements, avg_size, n_farm, 
         # acres_farms, acres_irrigated, pct_irrigated, cows, cows_per_farm, horses, pop, male, female, 
        # enrolled, pct_enrolled, urban_pop, pct_urban, illiterate, pct_illiterate
reg_years1 <- reg_years %>%
  mutate(mod = map(data, ~ lm(pct_enrolled ~ avg_size + avg_value_implements + n_farm + pct_irrigated + cows_per_farm + pct_urban, data = .)),
         reg_results = map(mod, ~ tidy(., conf.int = TRUE)),
         avg_size_coef = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% 
                                   pull(estimate)),
         avg_size_upper = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% 
                                    pull(conf.high)),
         avg_size_lower = map_dbl(reg_results, ~ filter(., term == "avg_size") %>% 
                                    pull(conf.low)),
         avg_value_implements_coef = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% 
                                               pull(estimate)),
         avg_value_implements_upper = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% 
                                                pull(conf.high)),
         avg_value_implements_lower = map_dbl(reg_results, ~ filter(., term == "avg_value_implements") %>% 
                                                pull(conf.low)),
         n_farm_coef = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(estimate)),
         n_farm_upper = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(conf.high)),
         n_farm_lower = map_dbl(reg_results, ~ filter(., term == "n_farm") %>% pull(conf.low)),
         pct_irrigated_coef = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(estimate)),
         pct_irrigated_upper = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(conf.high)),
         pct_irrigated_lower = map_dbl(reg_results, ~ filter(., term == "pct_irrigated") %>% pull(conf.low)),
         cows_per_farm_coef = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(estimate)),
         cows_per_farm_upper = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(conf.high)),
         cows_per_farm_lower = map_dbl(reg_results, ~ filter(., term == "cows_per_farm") %>% pull(conf.low)),
         pct_urban_coef = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(estimate)),
         pct_urban_upper = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(conf.high)),
         pct_urban_lower = map_dbl(reg_results, ~ filter(., term == "pct_urban") %>% pull(conf.low))
  )

@@

  select(YEAR, coef, lower, upper) %>%

@@

  tab_header(title = "Title",
             subtitle = "With 95% Confidence Interval") %>%
  cols_label(YEAR = "Year", coef = "Migrant Coefficient", 
             lower = "Lower Bound", upper = "Upper Bound") %>%
